Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-19 paper/Paper.tex

\subsection{TokenCreation}
\begin{verbatim}
contract TokenCreationInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFueled;
    address public privateCreation;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

    function TokenCreation(uint _minValue, uint _closingTime);
    function createTokenProxy(address _tokenHolder) returns (bool success);
    function refund();
    function divisor() returns (uint divisor);

@@

The integer \verb|minValue| is the number of wei which are needed to be received by the DAO in order to get funded.

@@

The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed. 
In order to interact with the contract the following functions can be used:

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateCreation|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

@@

    // End of token creation, in Unix time
    uint public closingTime;
    // Minimum fueling goal of the token creation, denominated in ether
    uint public minValue;
    // True if the DAO reached its minimum fueling goal, false otherwise
    bool public isFueled;
    // For DAO splits - if privateCreation is 0, then it is a public token
    // creation, otherwise only the address stored in privateCreation is
    // allowed to create tokens
    address public privateCreation;
    // hold extra ether which has been sent after the DAO token
    // creation rate has increased
    ManagedAccount public extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum fueling goal and the
    /// end of the Token Creation
    /// @param _minValue Token Creation minimum fueling goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Creation
    /// @param _privateCreation Zero means that the creation is public.  A
    /// non-zero address represents the only address that can create Tokens
    /// (the address can also create Tokens on behalf of other accounts)
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenCreation(
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

@@

contract TokenCreation is TokenCreationInterface, Token {
    function TokenCreation(uint _minValue, uint _closingTime, address _privateCreation) {
        closingTime = _closingTime;
        minValue = _minValue;
        privateCreation = _privateCreation;
        extraBalance = new ManagedAccount(address(this));
    }

@@

            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[_tokenHolder] += msg.value;
            CreatedToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFueled) {
                isFueled = true;
                FuelingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

@@

    /// @dev Constructor setting the Curator and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Creation
    /// @param _curator The Curator
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _proposalDeposit The deposit to be paid for a regular proposal
    /// @param _minValue Minimal value for a successful DAO Token Creation
    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Creation
    /// @param _privateCreation If zero the DAO Token Creation is open to public, a
    /// non-zero address means that the DAO Token Creation is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _curator,
        //  DAO_Creator _daoCreator,
        //  uint _proposalDeposit,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateCreation
    ) TokenCreation(_minValue, _closingTime, _privateCreation) {

        curator = _curator;
        daoCreator = _daoCreator;
        proposalDeposit = _proposalDeposit;
        rewardAccount = new ManagedAccount(address(this));
        DAOrewardAccount = new ManagedAccount(address(this));
        if (address(rewardAccount) == 0)
            throw;
        if (address(DAOrewardAccount) == 0)
            throw;
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length = 1; // avoids a proposal with ID 0 because it is used

@@

contract DAO_Creator {
    function createDAO(
        address _curator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime
    ) returns (DAO _newDAO) {

        return new DAO(
            _curator,
            DAO_Creator(this),
            _proposalDeposit,
            _minValue,
            _closingTime,
            msg.sender
        );
    }
}
\end{verbatim}

>>>>

\subsection{TokenCreation}
\begin{verbatim}
contract TokenCreationInterface {
    uint public closingTime;   
    uint public minTokensToCreate;
    bool public isFueled;
    address public privateCreation;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

    function TokenCreation(uint _minTokensToCreate, uint _closingTime);
    function createTokenProxy(address _tokenHolder) returns (bool success);
    function refund();
    function divisor() returns (uint divisor);

@@

The integer \verb|minTokensToCreate| is the number of wei-equivalent tokens which are needed to be created by the DAO in order to be considered fueled.

@@

The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minTokensToCreate|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed. 
In order to interact with the contract the following functions can be used:

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minTokensToCreate|
 \item \verb|closingTime|
 \item \verb|privateCreation|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

@@

    // End of token creation, in Unix time
    uint public closingTime;
    // Minimum fueling goal of the token creation, denominated in tokens to
    // be created
    uint public minTokensToCreate;
    // True if the DAO reached its minimum fueling goal, false otherwise
    bool public isFueled;
    // For DAO splits - if privateCreation is 0, then it is a public token
    // creation, otherwise only the address stored in privateCreation is
    // allowed to create tokens
    address public privateCreation;
    // hold extra ether which has been sent after the DAO token
    // creation rate has increased
    ManagedAccount public extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum fueling goal and the
    /// end of the Token Creation
    /// @param _minTokensToCreate Minimum required wei-equivalent tokens
    ///        to be created for a successful DAO Token Creation
    /// @param _closingTime Date (in Unix time) of the end of the Token Creation
    /// @param _privateCreation Zero means that the creation is public.  A
    /// non-zero address represents the only address that can create Tokens
    /// (the address can also create Tokens on behalf of other accounts)
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenCreation(
        //  uint _minTokensTocreate,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

@@

contract TokenCreation is TokenCreationInterface, Token {
    function TokenCreation(
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation) {

        closingTime = _closingTime;
        minTokensToCreate = _minTokensToCreate;
        privateCreation = _privateCreation;
        extraBalance = new ManagedAccount(address(this), true);
    }

@@

            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[_tokenHolder] += msg.value;
            CreatedToken(_tokenHolder, token);
            if (totalSupply >= minTokensToCreate && !isFueled) {
                isFueled = true;
                FuelingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

@@

    /// @dev Constructor setting the Curator and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Creation
    /// @param _curator The Curator
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _proposalDeposit The deposit to be paid for a regular proposal
    /// @param _minTokensToCreate Minimum required tokens to be created
    ///        for a successful DAO Token Creation
    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Creation
    /// @param _privateCreation If zero the DAO Token Creation is open to public, a
    /// non-zero address means that the DAO Token Creation is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _curator,
        //  DAO_Creator _daoCreator,
        //  uint _proposalDeposit,
        //  uint _minTokensToCreate,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    ) TokenCreation(_minTokensToCreate, _closingTime, _privateCreation) {

        curator = _curator;
        daoCreator = _daoCreator;
        proposalDeposit = _proposalDeposit;
        rewardAccount = new ManagedAccount(address(this), false);
        DAOrewardAccount = new ManagedAccount(address(this), false);
        if (address(rewardAccount) == 0)
            throw;
        if (address(DAOrewardAccount) == 0)
            throw;
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length = 1; // avoids a proposal with ID 0 because it is used

@@

contract DAO_Creator {
    function createDAO(
        address _curator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime
    ) returns (DAO _newDAO) {

        return new DAO(
            _curator,
            DAO_Creator(this),
            _proposalDeposit,
            _minTokensToCreate,
            _closingTime,
            msg.sender
        );
    }
}
\end{verbatim}
